---
title: "Who's that"
subtitle: "Mandarin reflexives"
author: "Ying Zhang"
institute: "Rutgers University"
date: "2025/04/05"
output:
  xaringan::moon_reader:
    css: ["rutgers", "rutgers-fonts"]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
# 1. Introduction

Reflexive pronouns (hence 'reflexives') are used for reference. Their referent is determined by their antecedents. For example, the reflexive *herself* in (1) refers to *Mary* since *Mary* is the antecedent of *herself*.

(1) Mary saw herself in the mirror.

There are two reflexives-- *ziji* and *taziji* in Mandarin which behave differently regarding their ability to take a non-local binder.

(2) John1 said Bill2 liked ziji(1/2).

(3) John1 said Bill2 liked taziji(*1/2).
---
# 2. Research questions
- Is *taziji* more likely to take a non-local binder in the elided structure?

- Does *ziji* behave the same in both the full structure and the elided structure regarding the choice of binder?
---
# 3. Materials and the design

There are 20 testing sentences for each participant. Each item includes two questions: Q1 and Q2. 

**Item**: 

A: Who did John say that Bill liked?

B: John said that Bill liked reflexive (full)./ Reflexive (elided).

**Q1**: Who do you think the reflexive refers to? John; Bill

**Q2** Can the reflexive refer to Bill/John?

**Dependent variable**: the choice of the binder, the local binder/Bill (1) and the non-local binder/John (0)

**Independent variables**: sentence type (full/elided) and survey/ reflexive type (taziji/ziji)
---
# 4. Data 

```{r}
#| label: setup
#| echo: false
#| message: false
#| warning: false
#| out-height: "75%"
#| out-width: "100%"
#| fig-asp: 0.4

library("tidyverse")
library("tidyr")
library("ds4ling")
library("here")
library("lme4")
library("broom")

dat_raw_1 <- read_csv(here("data", "raw", "survey_data.csv"))

head(dat_raw_1)
```
---
# 4. Tidy the data?
```{r}
#| label: tidy
#| echo: false
#| message: false
#| warning: false
#| out-height: "75%"
#| out-width: "100%"
#| fig-asp: 0.4

dat_raw <- read_csv(here("data", "raw", "survey_data_2.csv"))

dat_raw$q1_time <- dat_raw$q1_1+
  +   dat_raw$q1_2+
  +   dat_raw$q1_3+
  +   dat_raw$q1_4+
  +   dat_raw$q1_5+
  +   dat_raw$q1_6+
  +   dat_raw$q1_7+
  +   dat_raw$q1_8+
  +   dat_raw$q1_9+
  +   dat_raw$q1_10+
  +   dat_raw$q1_11+
  +   dat_raw$q1_12+
  +   dat_raw$q1_13+
  +   dat_raw$q1_14+
  +   dat_raw$q1_15+
  +   dat_raw$q1_16+
  +   dat_raw$q1_17+
  +   dat_raw$q1_18+
  +   dat_raw$q1_19+
  +   dat_raw$q1_20

dat_raw$q1_per <- dat_raw$q1_time / 20
dat_raw$q1_logit <- log((dat_raw$q1_per)/(1-dat_raw$q1_per))

dat_raw |> 
 relocate(q1_per, q1_logit, .after = sentence)
```
---
# 5. The plot 
```{r}
#| label: plot
#| echo: false
#| message: false
#| warning: false
#| out-height: "80%"
#| out-width: "100%"
#| fig-asp: 0.7
dat_raw |> 
  ggplot() +
  aes(x = sentence, y = q1_logit, fill = survey) +
  geom_boxplot()
```
---
# 6. The model
```{r}
#| label: mod
#| echo: true
#| message: false
#| warning: false

mod1<- lm(q1_logit ~ sentence * survey, data = dat_raw)
summary(mod1)

```
---
# 6. The model

```{r}
#| echo: true
#| message: false
#| warning: false

mod1_summary <- tidy(mod1)
knitr::kable(mod1_summary)
```
---
# 7. The issue
q2_logit is ***infinite***!
```{r}
#| echo: false
#| message: false
#| warning: false
  
dat_raw$q2_time <- dat_raw$q2_1+
  dat_raw$q2_2+
  dat_raw$q2_3+
  dat_raw$q2_4+
  dat_raw$q2_5+
  dat_raw$q2_6+
  dat_raw$q2_7+
  dat_raw$q2_8+
  dat_raw$q2_9+
  dat_raw$q2_10+
  dat_raw$q2_11+
  dat_raw$q2_12+ 
  dat_raw$q2_13+
  dat_raw$q2_14+
  dat_raw$q2_15+
  dat_raw$q2_16+
  dat_raw$q2_17+
  dat_raw$q2_18+
  dat_raw$q2_19+
  dat_raw$q2_20

dat_raw$q2_per <- dat_raw$q2_time / 20
dat_raw$q2_logit <- log((dat_raw$q2_per)/(1-dat_raw$q2_per))

dat_raw |> 
  relocate(q1_per, q1_logit, q2_per, q2_logit, .after = sentence)
```
---
# 8. Change the model?
- Since the dependent variables are binary responses, the logistic regression can be a better choice.

- Given that a single participant gives 40 data point, a mixed-effects model should be used. THe fixed effects are the sentence type and the survey type. The random effect is the subject/participant. 

- The ***issue***: for each item, there is the corresponding number of response. However, I just haven't figured out what to do there are 40 items.
